--- 
title: "CCC192 UPF 2017/1"
author: "Marcio Nicolau and Carlos Hölbig"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Conteúdo e exemplos da disciplina CCC192 UPF 2017/1"
---

# Conteúdos

1. Revisão Estatística Básica (Laboratório)

2. Gráficos no R (Laboratório)

3. Gráficos interativos no R (Laboratório)

4a. Modelo de Simulação (Teoria)

4b. Modelo e Simulação (Laboratório)

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

For now, you have to install the development versions of **bookdown** from Github:

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
